The Weakly Nonlinear Magnetorotational Instability in a thin-gap Taylor Couette flow

### 2016-10-04 paper/thingap_mri_paper.tex
two ways to compute nablasq

\section{Weakly Nonlinear Analysis}

@@

Here we detail the perturbation analysis described in Section \ref{sec:equations}. The linear system is described by Equation \ref{eq:unperturbed_matrix_equations}, where

@@

@@

>>>>

\section{Weakly Nonlinear Analysis}\label{sec:wnl}

@@

Here we detail the perturbation analysis described in Section \ref{sec:wnl}. The perturbation series is described by Equations \ref{eq:ordere} - \ref{eq:ordere3}, where

@@

\beq
\widetilde{\mathcal{L}}_1 =  \mathcal{L}_1 + 2\mathcal{L}_2\partial_z + 3\mathcal{L}_3\partial_z^2 + 4\mathcal{L}_4\partial_z^3
\eeq

\beq
\widetilde{\mathcal{L}}_2 = \mathcal{L}_2 + 3\mathcal{L}_3\partial_z + 6\mathcal{L}_4\partial_z^2
\eeq

@@

Once perturbed, the system is solved for successive orders of $\epsilon$ (Equations \ref{eq:ordere} - \ref{eq:ordere3}). $\mathcal{O}(\epsilon)$ is the linear system. At $\mathcal{O}(\epsilon^2)$, first-order MRI modes nonlinearly interact with themselves and with their complex conjugates, and so the term $\mathbf{N}_2$ in Equation \ref{eq:ordere2} has the form

\beq
\mathbf{N}_2 = |\alpha|^2 \mathbf{N}_{20} + \alpha^2 \mathbf{N}_{22} e^{2 i k_c z}
\eeq

(see Appendix \ref{app:nonlinear_terms} for the full form of $\mathbf{N}_{20}$ and $\mathbf{N}_{22}$).
